ML Estimation of Matrix t Distributions with Expectation Maximization

### 2016-12-11 paper.tex
Change abstract
Put what we do on top.

\begin{abstract}
Matrix--$t$ distribution has applications in various areas of applied statistics, including recommendation systems, remote sensing, etc. In this article we provide an expectation-maximization (EM) formulae for the maximum likelihood estimation of matrix--$t$ distributions and discuss their practical implementation.
\end{abstract}

>>>>

\begin{abstract}
We provide expectation-maximization (EM) formulae for the maximum
likelihood estimation of matrix--$t$ distributions and discuss their
practical implementation.  The result can be applied to problems where
the parameters of a matrix--$t$ distribution need to be obtained from
data, such as the design of recommendation systems, or remote sensing
algorithms.
\end{abstract}
